A large-scale analysis of racial disparities in police stops across the United

### 2019-12-10 lib/paper_results.Rmd

```{r disparity-state-thresholds-plot, fig.height=5, fig.width=10}
disp$state$threshold$prior_scaling_factor_1$plots$aggregate + theme(legend.position = "none")
```

>>>>

```{r disparity-state-thresholds-plot, fig.height=5, fig.width=10}
disp$state$threshold$prior_scaling_factor_1$plots$aggregate + 
  theme(
    legend.position = "none",
    plot.title = element_blank()
  )
```
